SimLTE: Simple Contrastive Learning for Long Text Embeddings

### 2022-12-15 paper/paper.tex
update abstract

\begin{document}
\maketitle
\begin{abstract}
%High-quality text embeddings are essential to various natural language understanding tasks especially for low-resource settings. 
%Existing methods are proposed for general text understanding but representations for long text are less explored.
%Basically, to have better embeddings for long text, a model should have the ability to recognize key information in a long text. 
%We introduce the $\our$ 
%To this end, we present \our, a simple unsupervised contrastive learning framework for long text embeddings in this paper. 
%Specifically, we pretrain a language model to distinguish if two texts have the same topic without any supervision. 
%The positive pairs are constructed by our key information redundancy assumption for long text.
Experimental results on five datasets show that \our~outperforms the state-of-the-art models by $3.9\%$ on classification tasks and $12.0\%$ macro-F1 in average respectively under general and few-shot text classification settings.

@@

\section{Introduction}
Generating high quality text embeddings for large documents is a long-standing open problem.
%The main difficulty is that models must be able to consider how text at the beginning of the document can influence text at the end of the document.
The recurrent connections in models like the LSTM \cite{} and GRU \cite{} allow information at all locations in the document to influence the final embedding,
but they are slow to train because the models must consider each word sequentially.
The transformer architecture \cite{} uses self-attention with no recurrent connections,
and so can be trained much faster than recurrent models.
This has led to the widespread use of language models like BERT \cite{} and ELMO \cite{} that are pre-trained on large scale web data.
Unfortunately, the memory requirements of self-attention scale as $O(n^2)$ and so are not suitable for long documents.
%Large scale pre-trained transformers like BERT \cite{} and ELMO \cite{} are currently state-of-the-art for many NLP tasks that require only short-term dependencies in text.
%These transformers do not handle long-term dependencies well, however, because they require $O(n^2)$ memory for the size of the context window.
The LongFormer \cite{} and BigBird \cite{} models allow larger-range dependencies by introducing improved attention mechanisms that reduce the memory requirements down to $O(n)$.
This previous research focuses on designing new model architectures suitable for large documents,
but in this paper we present the $\our$ training procedure that can work with any model architecture.
%All of this previous research focuses on designing new model architectures.
%Our paper introduces a new training method called the $\our$ that works for any model architecture.

$\our$ is the first unsupervised training method designed specifically for large documents.
Previous methods for training on large documents either require supervision \cite{} or use the masked language modeling (MLM) technique \cite{}.
In MLM, we replace a token from the input text with a special ``mask'' token and train the model to predict which token was removed.
The MLM pretraining method has been shown to work well for short-text documents \cite{},
but we argue that it sub-optimal for large documents because most of the information for predicting the masked token is available near the token.
The $\our$ pretraining technique is designed to force the model to learn long range dependencies within a document.
Specifically, $\our$ uses contranstive learning,
and our key contribution is a new method for generating the positive samples for contrastive learning (see Figure \ref{} above).
%The most similar work to our own is the \texttt{SimCSE} method which uses contrastive learning to pre-train text models,

@@

Our paper is organized as follows.
In Section \ref{sec:method} we formally define the contrastive learning problem and our novel $\our$ training method.
%We highlight how our $\our$ method improves on related contrastive learning frameworks like \texttt{SimCSE}
In Section \ref{sec:experiments} we develop a new experimental evaluation procedure for large documents.
We describe the first pre
We conclude in \ref{sec:conclusion} by emphasizing that all of our models and datasets are open source.

@@

\begin{figure}
%\includegraphics[width=\columnwidth]{fig/simlte_.pdf}
\caption{
    Need a detailed explanation of SimLTE here.
}
\vspace{-5mm}
\label{overall}
\end{figure}

>>>>

\begin{document}
\maketitle
\begin{abstract}
%High-quality text embeddings are essential to various natural language understanding tasks especially for low-resource settings. 
%Existing methods are proposed for general text understanding but representations for long text are less explored.
%Basically, to have better embeddings for long text, a model should have the ability to recognize key information in a long text. 
%We introduce the $\our$ 
%To this end, we present \our, a simple unsupervised contrastive learning framework for long text embeddings in this paper. 
%Specifically, we pretrain a language model to distinguish if two texts have the same topic without any supervision. 
%The positive pairs are constructed by our key information redundancy assumption for long text.
% Experimental results on five datasets show that \our~outperforms the state-of-the-art models by $3.9\%$ on classification tasks and $12.0\%$ macro-F1 in average respectively under general and few-shot text classification settings.

This paper presents $\our$, the first unsupervised pretraining
method designed specifically for long text (e.g.,~documents, paragraphs).
$\our$ uses the contrastive learning framework, and our main contribution is a simple data augmentation technique for generating similar document pairs.
A key advantage of $\our$ over other techniques for working with
long text is that it requires no changes to model architecture, and so it is widely applicable.
We use $\our$ pretraining to improve the embeddings of previously
developed state-of-the-art models.
On standard classification datasets, $\our$ improves all baseline
models, with an average improvement of $3.9\%$ macro F1 score.
We also consider a few-shot setting where we show an average
improvement of $12.0\%$.

@@

\section{Introduction}
Generating high quality text embeddings for long text is a long-standing open problem.
%The main difficulty is that models must be able to consider how text at the beginning of the document can influence text at the end of the document.
The recurrent connections in models like the LSTM \cite{} and GRU \cite{} allow information at all locations in the document to influence the final embedding,
but they are slow to train because the models must consider each word sequentially.
The transformer architecture \cite{} uses self-attention with no recurrent connections,
and so can be trained much faster than recurrent models.
This has led to the widespread use of language models like BERT \cite{} and ELMO \cite{} that are pre-trained on large scale web data.
Unfortunately, the memory requirements of self-attention scale as $O(n^2)$ and so are not suitable for long documents.
%Large scale pre-trained transformers like BERT \cite{} and ELMO \cite{} are currently state-of-the-art for many NLP tasks that require only short-term dependencies in text.
%These transformers do not handle long-term dependencies well, however, because they require $O(n^2)$ memory for the size of the context window.
The LongFormer \cite{} and BigBird \cite{} models allow larger-range dependencies by introducing improved attention mechanisms that reduce the memory requirements down to $O(n)$.
This previous research focuses on designing new model architectures suitable for long text,
but in this paper we present the $\our$ training procedure that can work with any model architecture.
%All of this previous research focuses on designing new model architectures.
%Our paper introduces a new training method called the $\our$ that works for any model architecture.

$\our$ is the first unsupervised training method designed specifically for long text.
Previous methods for training on long text either require supervision \cite{} or use the masked language modeling (MLM) technique \cite{}.
In MLM, we replace a token from the input text with a special ``mask'' token and train the model to predict which token was removed.
The MLM pretraining method has been shown to work well for short-text documents \cite{},
but we argue that it sub-optimal for long text because most of the information for predicting the masked token is available near the token.
The $\our$ pretraining technique is designed to force the model to learn long range dependencies within a document.
Specifically, $\our$ uses contranstive learning,
and our key contribution is a new method for generating the positive samples for contrastive learning (see Figure \ref{} above).
%The most similar work to our own is the \texttt{SimCSE} method which uses contrastive learning to pre-train text models,

@@

Our paper is organized as follows.
In Section \ref{sec:method} we formally define the contrastive learning problem and our novel $\our$ training method.
%We highlight how our $\our$ method improves on related contrastive learning frameworks like \texttt{SimCSE}
In Section \ref{sec:experiments} we develop a new experimental evaluation procedure for long text.
We describe the first pre
We conclude in \ref{sec:conclusion} by emphasizing that all of our models and datasets are open source.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{fig/simlte.pdf}
\caption{Overall framework of \our. The long text is randomly divided into two exclusive subsets of sentences and the two subsets work as positive pairs for contrastive learning. Other instances in the same batch are used as negatives.
}

\label{overall}
\end{figure}
